On Secure Delegation of SampBQP with a Classical Client

### 2019-12-23 qpip.tex
Make editorial changes

\begin{observation}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

@@

	We claim that the following protocol does what is required:
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies; $m$ for output and $n$ for checking
			\State $c\gets0$
			\For{$i\gets1, N$}
			    \If{Register is for checking}
			    \State The verifier runs \autoref{AlgGroundStateCheck} on the register
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Register is for outputting}
			    \State The verifier measures the clock register
			    \If{measurement result $\geq\frac{T}{2}$}
			        \If{$y$ isn't set}
			            $y\gets$ Measure the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State Measure the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y$ is set}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends.

	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state after the random permutation as

@@

	Let $\tilde{\Pi}$ be some fixed permutation. Then it is easy to check that

@@

	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.

>>>>

\begin{observation}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
	\Ethan{Maybe give the protocol a name then?}
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

@@

	We claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_1$ protocol}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies; $m$ for output and $n$ for checking
			\State $c\gets0$
			\For{$i\gets1, N$}
			    \If{Register is for checking}
			    \State The verifier runs \autoref{AlgGroundStateCheck} on the register
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Register is for outputting}
			    \State The verifier measures the clock register
			    \If{measurement result $\geq\frac{T}{2}$}
			        \If{$y$ isn't set}
			            $y\gets$ Measure the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State Measure the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y$ is set}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends.

	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers.
	We can see a random permutation as a classical mix over all possible permutations of $\sigma$; mathematically, it can be written as:

@@

	Now we verify that $\sigma'$ is indeed permutation-invariant.
	Let $\tilde{\Pi}$ be some fixed permutation, then clearly:

@@

	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.
	\Ethan{Change this, since we changed the algorithm}
